\newpage
\begin{thebibliography}{99}

\bibitem{eeye} 
\emph{``ANALYSIS: .ida "Code Red" Worm''}
eEye. July 17, 2001\\
\url{https://web.archive.org/web/20110722192419/http://www.eeye.com/Resources/Security-Center/Research/Security-Advisories/AL20010717}

\bibitem{bullet}
\emph{``Microsoft Security Bulletin MS01-033 - Critical''}
Microsoft. June 18, 2001\\
\url{https://docs.microsoft.com/en-us/security-updates/securitybulletins/2001/ms01-033}

\bibitem{caida} Moore, David \& Shannon, Colleen \& Brown, Jeffery. 
\emph{``Code-Red: a case study on the spread and victims of an Internet worm''}
CAIDA.\\
\url{http://www.caida.org/publications/papers/2002/codered/codered.pdf}

\bibitem{two-factor} Cliff Changchun Zou, Weibo Gong, Don Towsley.
\emph{``Code Red Worm Propagation Modeling and Analysis.''}
Dept. Electrical \& Computer Engineering Univ. Massachusetts Amherst, MA\\
\url{http://www.cs.ucf.edu/~czou/research/codered.pdf}

\bibitem{selke} Sarah Sellke, Ness B. Shroff, and Saurabh Bagchi.
\emph{``Modeling and Automated Containment of Worms.''}
School of Electrical and Computer Engineering Purdue University\\
\url{https://ieeexplore.ieee.org/document/4358715/}

\bibitem{ce}
\emph{``Malicious Code Attacks Had \$13.2 Billion Economic Impact in 2001.''}
Computer Economics. September, 2002\\
\url{https://www.computereconomics.com/article.cfm?id=133}

\bibitem{sans} Schauer, Renee C..
\emph{``The Mechanisms and Effects of the Code Red Worm.''}
Sans Institute. 2001\\
\url{https://www.sans.org/reading-room/whitepapers/dlp/the-mechanisms-and-effects-of-the-code-red-worm-87}

\bibitem{cisco}
\emph{``Code Red Worm - Customer Impact.''}
Cisco. July 20, 2001\\
\url{https://tools.cisco.com/security/center/content/CiscoSecurityAdvisory/cisco-sa-20010720-code-red-worm}

\bibitem{eich} K. Eichman.
\emph{``Possible CodeRed Connection Attempts.''}
July 20, 2001\\
\url{http://lists.jammed.com/incidents/2001/07/0159.html}

\bibitem{gold} D. Goldsmith. 
\emph{``Possible CodeRed Connection Attempts.''}
July 20, 2001\\
\url{http://lists.jammed.com/incidents/2001/07/0149.html}

\bibitem{sans-acl} Dennis Eck.
\emph{``Access Control Lists to Protect a Network from Worm/DoS Attacks.''}
Sans Institute. December 4, 2003\\
\url{https://www.giac.org/paper/gsec/3551/access-control-lists-protect-network-worm-dos-attacks/105776}

\bibitem{sans-acl} William Geige.
\emph{``Proactively Guarding Against Unknown Web Server Attacks.''}
Sans Institute.\\
https://www.giac.org/paper/gsec/1153/proactively-guarding-unknown-web-server-attacks/102250
\end{thebibliography}
